Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-03-15 Paper/gammaRays.tex
Drafted table with observation results

\begin{figure}
	\centering
	\includegraphics[width=0.49\textwidth]{sampleLightCurve}
	\caption{
		High and low energy light curves produced by the geometrical model. Parameter values are the same as discussed in the section \ref{sec:parameters}. Redshift $z = 1$. Observer's off-axis angle $\chi = 0.01$.
	}
	\label{fig:sampleLightCurve}
\end{figure}

Finally, our assumption is able to explain the non-trivial stretching factor of the GRB 090926A. Detailed computations will be described in the following sections, but you can see the main idea on the figure \ref{fig:modelOverview}. The computations confirm that this qualitative picture is indeed correct. You can see a sample light curve on the figure \ref{fig:sampleLightCurve}, and predicted distribution of stretching factors on the figure \ref{fig:kappaDistribution}.

@@

@@

>>>>

\begin{figure}
	\centering
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{sampleLightCurveLogNegative}
		\label{fig:sampleLightCurveLogNegative}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{sampleLightCurveLogPositive}
		\label{fig:sampleLightCurveLogPosivie}
	\end{subfigure}
	\caption{
		High and low energy light curves produced by the geometrical model. Parameter values are the same as discussed in the section \ref{sec:parameters}. Redshift $z = 1$. Observer's off-axis angles are $\chi = 0$ for the left figure, and $\chi = 0.01$ for the right one.
	}
	\label{fig:sampleLightCurves}
\end{figure}

Finally, our assumption is able to explain the non-trivial stretching factor of both GRBs 090902B and 090926A. Detailed computations will be described in the following sections, but you can see the main idea on the figure \ref{fig:modelOverview}. The computations confirm that this qualitative picture is indeed correct. You can see a sample light curves on the figure \ref{fig:sampleLightCurves}, and predicted distribution of stretching factors on the figure \ref{fig:kappaDistribution}.

@@

Out of 19 bursts studied, only 4 have at least 10 high energy events remaining after filtering, and thus eligible for the computation of stretching factors. The results of this computation are shown on figures \ref{fig:grb080916C}, \ref{fig:grb090510}, \ref{fig:grb090902B}, \ref{fig:grb090926A}.

@@

\begin{table}
	\centering
	\small
	\begin{tabular}{ l | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] | S[table-format=2.3]@{\; -- \;}S[table-format=2.3] }
		\multicolumn{1}{ c |}{GRB} & \multicolumn{2}{ c |}{$1\sigma$} & \multicolumn{2}{ c |}{$2\sigma$} & \multicolumn{2}{ c |}{$3\sigma$} & \multicolumn{2}{ c |}{$4\sigma$} & \multicolumn{2}{ c }{$5\sigma$} \\
		\hline
		080825C	&	1.04  & 2.24	&	0.67 & 3.32	&	0.42 & 5.83	&	0.19 & 14.9		&	0.087 & 35.7	\\
		090501	&	0.58  & 1.1		&	0.43 & 1.61	&	0.32 & 2.29	&	0.22 &  3.03	&	0.17  &  5.11	\\
		090902B	&	0.629 & 0.635	&	0.36 & 0.89	&	0.23 & 1.57	&	0.13 &  2.87	&	0.084 &  4.56	\\
		090926A &	2.61  & 3.33	&	1.99 & 6.62	&	1.34 & 9.15	&	0.73 & 13.5		&	0.48  & 19.4
	\end{tabular}
	\caption{Caption}
	\label{tab:observationResults}
\end{table}

%\begin{table}
%	\centering
%	\small
%	\begin{tabular}{ l | S[table-format=1.3] | S[table-format=1.3] | S[table-format=1.3] | S[table-format=1.3] | S[table-format=1.3]}
%		\multicolumn{1}{ c |}{GRB Name} & $1\sigma$ & $2\sigma$ & $3\sigma$ & $4\sigma$ & $5\sigma$ \\
%		%\multicolumn{1}{ c |}{Name}& $\mathrm{MET,\ sec}$ & $\mathrm{J2000,\ deg}$ & $\mathrm{J2000,\ deg}$ & $\mathrm{deg}$ & $\mathrm{sec}$ & $\mathrm{sec}$ \\
%		\hline
%		080916C	&	1.042	&	1.200	&	1.300	&	1.400	&	1.500
%	\end{tabular}
%	\caption{Burst data used in our study. The first row contains the corresponding \texttt{GRBurst} class variable names. The data is taken from the tables 2 and 4 of \cite{Ackermann:2013zfa}. \url{https://github.com/maxitg/GammaRays/blob/master/GRObservations/bursts}}
%	\label{tab:observationResults}
%\end{table}
